### 2021-03-18 paper.Rmd
notes to urusla

>>>>

Notes to Ursula:

- The basis space constrained by the orthonormality condition forms a Stiefel manifold, which is a sphere in 1D case and a torus in 2D case (I have one sentence for that in the notation section).
- The space plot with tour path embedded are `figure/notation-1d-space.pdf` and `figure/notation-2d-space.pdf` - let me know if this is what you want
